---
title: "Sc_RNAseq_GAL9"
author: "Paul Marcoux"
date: today
date-format: "YYYY-MM-DD"
format: 
  html:
    page-layout: full
    toc: true
    toc-depth: 3
    toc-location: left
    code-fold: true
    echo: false
    code-summary: "Show code"
    code-tools: true
    theme: cosmo
    embed-resources: false
    number-sections: true
execute:
  warning: false
  message: false
  freeze: auto
  fig-width: 12
  column: page
---

# Analyse of B-NHL scRNAseq data

## Open Data & Review

```{r}
# #| include: false
library(here)
library(gtools)
library(Seurat)
source(here('src/00_Open_metadata.R'))
source(here('src/01_Open_sc_files.R'))
```

```{r}
Data_info_patients <- Metadata_All |> select(Sample_code,Origin,RD,Disease) |> distinct() 

Data_info_patients <- Data_info_patients[mixedorder(Data_info_patients$Sample_code), ]
knitr::kable(Data_info_patients)

```

## All Cell types

### Umap

```{r}
DimPlot(AllSample,
        reduction = "umap_all",
        label = FALSE,
        pt.size = 0.01,
        raster = FALSE,
        group.by = "Sample_code",
        alpha = 0.3
) 
DimPlot(AllSample,
        reduction = "umap_all",
        label = FALSE,
        pt.size = 0.01,
        raster = FALSE,
        group.by = "Cell_type",
        alpha = 0.3
) 
```

### Cell Type repartition per sample

```{r CellType repartition per sample }
pochi::MetaDataPlot(AllSample, group.by = "Cell_type", split.by = "Sample_code", as.freq = T) +
  labs(
    title = "",
    x = "", # Éviter de répéter des informations évidentes
    y = "Frequency",
    fill = "Cell Type"
  ) +
  labs(fill = "Cell Type") +
  theme_blood() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1, face = "bold")) # Inclinaison des labels
```

### GAL 1/3/9 by disease

**Expression of GAL9 increase in tFl/DLBCL compared to FL.**

```{r}
VlnPlot(AllSample,
            features = c("LGALS1","LGALS3","LGALS9"),
            group.by = "Disease",
            pt.size = 0,
            raster = FALSE)
```

**What Cell type are expressing GAL1/3/9 ?**

**GAL1 is expressed mostly by Monocytes and NK Cells. Only GAL gene expressed by CD8 Tcells**

```{r}
VlnPlot(AllSample,
        features = c("LGALS1"),
        group.by = "Disease",
        split.by = "Cell_type",
        pt.size = 0,
        raster = FALSE)
```

```{r}
VlnPlot(AllSample,
        features = c("LGALS3"),
        group.by = "Disease",
        split.by = "Cell_type",
        pt.size = 0,
        raster = FALSE)
```

**GAL9 is expressed mostly by Monocytes, and to a lesser extent by CD4 T-Cells and NK Cells.**

```{r}
VlnPlot(AllSample,
        features = c("LGALS9"),
        group.by = "Disease",
        split.by = "Cell_type",
        pt.size = 0,
        raster = FALSE)
```

## Monocytes Only

```{r}
AllSample_subset_monocytes <- LoadSeuratRds(here("~/Postdoc/R/ScRNA_Barcelona/data/Seurat_obj/AllSample_subset_monocytes_cleaned_cca_rpca_integrated.rds"))
```

#### Umap of Monocytes only by cluster and disease

**Monocytes only from PBMC samples.**

```{r}
DimPlot(AllSample_subset_monocytes,
            reduction = "umap.rpca",
            group.by = "Origin",
            pt.size = 0.01,
            raster = FALSE,
        label.size = 3) +
  plot_layout(guides = "collect")
```

-   Filtering of low quality cells, Bcells, Tcells.

-   Very few Monocytes from DLBCL samples -\> Removed from analysis.

-   RPCA integration

**Good integration between FL and tFL Samples**

```{r}
DimPlot(AllSample_subset_monocytes,
            reduction = "umap.rpca",
            group.by = "Disease",
            pt.size = 0.01,
            raster = FALSE) +
  plot_layout(guides = "collect")
```

### GAL 1/3/9 in Monocytes

```{r}
#| warning: false
VlnPlot(AllSample_subset_monocytes,
        features = c("LGALS1","LGALS3","LGALS9"),
        group.by = "Disease",
        pt.size = 0,
        raster = FALSE)&
  scale_fill_manual(values = c("#f8766d","#00ba38"))  # Custom fill colors_response_type

  
```

### Identification of Monocytes

**11 clusters identify**

```{r}
DimPlot(AllSample_subset_monocytes,
            reduction = "umap.rpca",
            group.by = "rpca_clusters",
            pt.size = 0.01,
            raster = FALSE) +
  plot_layout(guides = "collect")
```

**DotPlot of Monocytes/Macrophages Markers**

```{r}
# 1. Define the canonical markers based on your DE results
myeloid_markers <- c(
  # Monocyte Lineage
  "CD14","CCR2", "VCAN", "S100A9", "S100A8","ANXA1",  # Cluster 4: Early Classical
  "F5",            
  "PADI4", "ALOX5AP", "RETN", "SLC2A3",      # Cluster 2: Mature Classical

  "IL1B", "CXCL8", "NLRP3", "TREM1",         # Cluster 1: Inflammatory Mac/Mono
  
  "ISG15", "IFIT1", "MX1", "SIGLEC1",        # Cluster 7: ISG-High (Interferon)
  


  # Macrophage-like

  "VSIG4", "CD9", "SMAD7", "OLR1",           # Cluster 0: Resident Mac
  "C1QA", "C1QB", "LIPA",            #  C1q+ Scavenging Mac
  
  # Non Classical
  "CDKN1C", "FCGR3A", "HES4", "RHOC",        # Cluster 3: Non-classical
  "SAT1", "HSPA6", "ITGAX", "LILRB2",        # Cluster 8: Activated Non-classical
  
  
  # Dendritic Cells
  "CLEC9A","C1orf54", "CADM1", "XCR1",       # Cluster 10: cDC1 (Villani et al. 2019)
  "CD1C", "FCER1A", "CLEC10A",               # Cluster 6: cDC2 (Villani et al. 2019)

  # Proliferation state
  "MKI67", "TOP2A", "BIRC5", "CENPF"     # Cluster 9: Cycling Myeloid
  
  
)
# 2. Factor Order
biological_order <- c(
  "Early Classical Monocytes", 
  "Proliferating Monocytes",
  "Mature Classical Monocytes", 
  "Activated Classical Monocytes", 
  "IFN-stimulated Monocytes",
  "CD14+ Intermediate Monocytes", 
  "CD16+ Transitional Monocytes",
  "CD16+ Non-classical Monocytes",
  "CD11c+ Non-classical Monocytes",
  "cDC1",
  "cDC2"
)


# 3. Generate the DotPlot
levels(AllSample_subset_monocytes) <- rev(biological_order)

DotPlot(AllSample_subset_monocytes, features = myeloid_markers, dot.scale = 5) + 
  RotatedAxis() + 
  scale_colour_gradient2(low = "blue", mid = "white", high = "red") +
  labs(title = "Myeloid Subset Canonical Markers", x = "Genes", y = "Cluster")+
      theme(
      axis.text.x = element_text(size = 8, face = "bold", color = "black"), # Labels des axes X
      axis.text.y = element_text(size = 8, face = "bold", color = "black"),
      axis.title = element_text(size = 8, face = "bold"),
      axis.title.y = element_text(size = 8, face = "bold", color = "black"), # Labels des axes X
      legend.title = element_text(size = 7, face = "bold"), # Titre de la légende
      legend.text = element_text(size = 6, face = "bold"),
      legend.box.spacing = unit(0.1, "cm"),
      legend.key.size = unit(0.4, "cm"))
levels(AllSample_subset_monocytes) <- (biological_order)


```

CLEC10A = CD301C FCGR3A = CD16 ITGAX = CD11c

```{r}
DimPlot(
  AllSample_subset_monocytes,
  reduction = "umap.rpca",
  combine = , label.size = 5,
  label = TRUE
)+
  theme_blood()
```

```{r}
pochi::MetaDataPlot(AllSample_subset_monocytes, group.by = "Cell_type_monocytes", split.by = "Disease", as.freq = T) +
  labs(
    title = "",
    x = "", # Éviter de répéter des informations évidentes
    y = "Frequency",
    fill = "Cell Type"
  ) +
  labs(fill = "Cell Type") +
  # scale_fill_brewer(palette = "GnBu", direction = -1) +
  # theme_blood() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1, face = "bold")) # Inclinaison des labels
```

#### Violin Plots of Monocytes Markers
**GAL1 **
```{r}
VlnPlot(AllSample_subset_monocytes, features = "LGALS1",pt.size = 0)
FeaturePlot(AllSample_subset_monocytes, features = "LGALS1",pt.size = 0.01, raster = FALSE,
            split.by = "Disease", reduction = "umap.rpca",) &
    scale_color_distiller(palette = "RdYlBu") 

VlnPlot(AllSample_subset_monocytes, features = "LGALS1",pt.size = 0,split.by = "Disease")&
  scale_fill_manual(values = c("#f8766d","#00ba38"))
```

**GAL3 **
```{r}
VlnPlot(AllSample_subset_monocytes, features = "LGALS3",pt.size = 0)
FeaturePlot(AllSample_subset_monocytes, features = "LGALS3",pt.size = 0.01, raster = FALSE,
            split.by = "Disease", reduction = "umap.rpca",) &
    scale_color_distiller(palette = "RdYlBu") 

VlnPlot(AllSample_subset_monocytes, features = "LGALS3",pt.size = 0,split.by = "Disease")&
  scale_fill_manual(values = c("#f8766d","#00ba38"))
```

**GAL9 **
```{r}
VlnPlot(AllSample_subset_monocytes, features = "LGALS9",pt.size = 0)
FeaturePlot(AllSample_subset_monocytes, features = "LGALS9",pt.size = 0.01, raster = FALSE,
            split.by = "Disease", reduction = "umap.rpca",) &
    scale_color_distiller(palette = "RdYlBu") 

VlnPlot(AllSample_subset_monocytes, features = "LGALS9",pt.size = 0,split.by = "Disease")&
  scale_fill_manual(values = c("#f8766d","#00ba38"))

```

## CD4 Tcells Only

```{r T cells R Object}
load(file = file.path(data_dir, 'Object_R/Seurat_obj_T_annoted.Robj'))
Tcells_joined <- JoinLayers(Tcells)

Tcells_joined$Disease <- factor(Tcells_joined$Disease, levels = c("FL", "tFL", "DLBCL"))

rm(Tcells)
```

```{r}
Tcells_TCD4 <- subset(Tcells_joined, subset = Cell_type == "CD4")

DimPlot(Tcells_TCD4,
        reduction = "umap",
        label = TRUE,
        pt.size = 0.01,
        raster = FALSE,
        alpha = 0.3)
```

```{r Dot Plot T cell cluster}
  markers <- c(
    "CD3D", "CD3E", "CD3G", "CD4", "CD8A", "CD8B2", "NCAM1", "NELL2", "TCF7", "LEF1", "CCR7", "PTPRC", "SELL", "IL7R", "B3GAT1", "SESN3", "CD28", "LTB", "TNFRSF4", "EOMES", "GZMA", "GZMB", "GZMK", "GZMH",
    "PRF1", "TOX", "TOX2", "HAVCR2", "LAG3", "TIGIT", "FASLG", "KLRB1", "ICOS", "CXCL13", "CXCR5", "PDCD1",
    "IL6R", "CD40LG", "FOXP3", "CTLA4", "IL2RA", "TYROBP", "TOP2A", "MKI67", "CX3CR1", "FCER1G", "BCL6"
  )

DotPlot(Tcells_TCD4, features = markers, assay = "RNA", dot.scale = 5) +
    RotatedAxis() + 
    scale_color_gradient2(low = "blue", mid = "white", high = "firebrick2") +
    labs(title = "Tcells Canonical Markers", x = "Genes", y = "Cluster")+
      theme(
      axis.text.x = element_text(size = 8, face = "bold", color = "black"), # Labels des axes X
      axis.text.y = element_text(size = 8, face = "bold", color = "black"),
      axis.title = element_text(size = 8, face = "bold"),
      axis.title.y = element_text(size = 8, face = "bold", color = "black"), # Labels des axes X
      legend.title = element_text(size = 7, face = "bold"), # Titre de la légende
      legend.text = element_text(size = 6, face = "bold"),
      legend.box.spacing = unit(0.1, "cm"),
      legend.key.size = unit(0.4, "cm"))
```

### Markers in T cells
**GAL1 is expressed in FL, tFL and  DLBCL samples whereas GAL9 is mostly expressed in DLBCL samples**
```{r}
VlnPlot(Tcells_TCD4,
        features = c("LGALS1","LGALS3","LGALS9"),
        group.by = "Disease",
        pt.size = 0,
        raster = FALSE)
```
**Expression of **
```{r}
VlnPlot(Tcells_TCD4,
        features = c("LGALS1","LGALS3","LGALS9"),
        group.by = "T_clusters",
        pt.size = 0.00,
        raster = FALSE)
```
**TIM3 and 41BB expressions are low but maybe expressed a bit more in Treg?**
```{r}
VlnPlot(Tcells_TCD4,
        features = c("HAVCR2","TNFRSF9"),
        group.by = "Disease",
        pt.size = 0.01,
        raster = FALSE)
```
```{r}
VlnPlot(Tcells_TCD4,
        features = c("HAVCR2","TNFRSF9"),
        group.by = "T_clusters",
        pt.size = 0.01,
        raster = FALSE)
```

### Treg only

```{r}
Tcells_TCD4_Treg <- subset(Tcells_joined, subset = T_clusters == "CD4_Treg")

VlnPlot(Tcells_TCD4_Treg,
        features = c("LGALS1","LGALS3","LGALS9"),
        group.by = "Disease",
        pt.size = 0,
        raster = FALSE
)

VlnPlot(Tcells_TCD4_Treg,
        features = c("HAVCR2","TNFRSF9"),
        group.by = "Disease",
        pt.size = 0.01,
        raster = FALSE)
```

## NK Only

```{r}


Origin_distribution <- pochi::MetaDataPlot(AllSample, group.by = "Cell_type", split.by = "Origin", as.freq = T) +
  labs(
    title = "",
    x = "", # Éviter de répéter des informations évidentes
    y = "Frequency",
    fill = "Cell Type"
  ) +
  labs(fill = "Cell Type") +
  # scale_fill_brewer(palette = "GnBu", direction = -1) +
  theme_blood() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1, face = "bold")) # Inclinaison des labels

Disease_distribution <- pochi::MetaDataPlot(AllSample, group.by = "Cell_type", split.by = "Disease", as.freq = T) +
  labs(
    title = "",
    x = "", # Éviter de répéter des informations évidentes
    y = "Frequency",
    fill = "Cell Type"
  ) +
  labs(fill = "Cell Type") +
  # scale_fill_brewer(palette = "GnBu", direction = -1) +
  theme_blood() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1, face = "bold")) # Inclinaison des labels

plot_grid(Origin_distribution, Disease_distribution,
          ncol = 2)

```

```{r}
Tcells_NK <- subset(Tcells_joined, subset = Cell_type == "NK")
Origin_distribution <- pochi::MetaDataPlot(Tcells_NK, group.by = "Cell_type", split.by = "Origin", as.freq = F) +
  labs(
    title = "",
    x = "", # Éviter de répéter des informations évidentes
    y = "Cells Number",
    fill = "Cell Type"
  ) +
  labs(fill = "Cell Type") +
  # scale_fill_brewer(palette = "GnBu", direction = -1) +
  theme_blood() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1, face = "bold")) # Inclinaison des labels

Disease_distribution <- pochi::MetaDataPlot(Tcells_NK, group.by = "Cell_type", split.by = "Disease", as.freq = F) +
  labs(
    title = "",
    x = "", # Éviter de répéter des informations évidentes
    y = "Numbers",
    fill = "Cell Type"
  ) +
  labs(fill = "Cell Type") +
  # scale_fill_brewer(palette = "GnBu", direction = -1) +
  theme_blood() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1, face = "bold")) # Inclinaison des labels

plot_grid(Origin_distribution, Disease_distribution,
          ncol = 2)

```

### Markers in NK

```{r}
VlnPlot(Tcells_NK,
        features = c("LGALS1"),
        group.by = "Disease",
        pt.size = 0,
        raster = FALSE
)

VlnPlot(Tcells_NK,
        features = c("LGALS3"),
        group.by = "Disease",
        pt.size = 0,
        raster = FALSE
)

VlnPlot(Tcells_NK,
        features = c("LGALS9"),
        group.by = "Disease",
        pt.size = 0,
        raster = FALSE
)
#TIM3
VlnPlot(Tcells_NK,
        features = c("HAVCR2"),
        group.by = "Disease",
        pt.size = 0,
        raster = FALSE
)

#41BB
VlnPlot(Tcells_NK,
        features = c("TNFRSF9"),
        group.by = "Disease",
        pt.size = 0,
        raster = FALSE
)
```

## Bcells Only

```{r}
load(here("~/Postdoc/R/SC_Flex_TALYIES_July2024/Object_R/Seurat_obj_B_annoted.Robj"))

```

```{r}
Metadata_Bcell <- AllBcells@meta.data %>%
    select(orig.ident, type, Lymphomatype,Cluster_name,Response_type_total) %>%
    mutate(Sample_code = gsub("\\.", "_", orig.ident)) %>%
    mutate(cell_id = gsub("\\.", "_", rownames(.))) %>%
    mutate(
      Sample_code = ifelse(Sample_code == "FL5_PB1", "FL5_PB1_3", Sample_code),
      Sample_code = ifelse(Sample_code == "FL6_PB1", "FL6_PB1_2", Sample_code)
    ) |> 
  mutate(B_cell_type = case_when(
    # Cluster_name == "Circulating_B_Cells" ~ "Circulating_B_Tumor_B_Cells",
    Cluster_name %in% c("tFL4_PB1_2","DLBCL6_LN1_2","DLBCL2_LN1_2") ~ "Proliferating_Tumor_B_Cells",
    Cluster_name == "Healthy_B_Cells" ~ "Healthy_B_Cells",
    Cluster_name == "KI67+_B_Cells" ~ "Proliferating_Tumor_B_Cells",
    TRUE ~ "Non_Prolif_Tumor_B_Cells"
  )) |> 
  mutate(Lymphomatype = factor(Lymphomatype, levels = c("FL","tFL","DLBCL")),
         Sample_code_paper = Sample_code,
         Sample_code_paper = recode(Sample_code_paper, !!!Replacement_table),
         Sample_code = factor(Sample_code, levels = Sample_order),
         type = if_else(type == "PB", "PBMC", type)
)

  AllBcells <- AddMetaData(AllBcells, metadata = Metadata_Bcell$orig.ident, col.name = "orig.ident")
  AllBcells <- AddMetaData(AllBcells, metadata = Metadata_Bcell$Sample_code_paper, col.name = "Sample_code_paper")
  AllBcells <- AddMetaData(AllBcells, metadata = Metadata_Bcell$Sample_code, col.name = "Sample_code")
  AllBcells <- AddMetaData(AllBcells, metadata = Metadata_Bcell$B_cell_type, col.name = "B_cell_type")
  AllBcells <- AddMetaData(AllBcells, metadata = Metadata_Bcell$type, col.name = "Origin")
  AllBcells <- AddMetaData(AllBcells, metadata = Metadata_Bcell$Lymphomatype, col.name = "Disease")
  
```

**Expression of GAL genes in all B are low**
```{r}
VlnPlot(AllBcells, features = c("LGALS1","LGALS3","LGALS9"),pt.size = 0,group.by = "Disease")
```

### BCells Umap

```{r}
DimPlot(AllBcells,
        reduction = "full.umap",
        label = FALSE,
        pt.size = 0.01,
        raster = FALSE,
        group.by = "Sample_code",
        alpha = 0.3
) 

FeaturePlot(AllBcells,
        reduction = "full.umap",
        features = "MKI67",
        pt.size = 0.01,
        raster = FALSE,
        alpha = 0.3
) 

DimPlot(AllBcells,
        reduction = "full.umap",
        label = FALSE,
        pt.size = 0.01,
        raster = FALSE,
        group.by = "B_cell_type",
        alpha = 0.3
) 

```

### B Cells repartition

```{r}
pochi::MetaDataPlot(AllBcells, group.by = "B_cell_type", split.by = "Sample_code", as.freq = T) +
  labs(
    title = "",
    x = "", 
    y = "Frequency",
    fill = "Cell Type"
  ) +
  labs(fill = "Cell Type") +
  theme_blood() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1, face = "bold")) # Inclinaison des labels

pochi::MetaDataPlot(AllBcells, group.by = "B_cell_type", split.by = "Sample_code", as.freq = F) +
  labs(
    title = "",
    x = "", 
    y = "Cell Numbers",
    fill = "Cell Type"
  ) +
  labs(fill = "Cell Type") +
  theme_blood() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1, face = "bold")) # Inclinaison des labels
```

### Markers in B Cells
**Expression of GAL genes in B cell types**
```{r}
VlnPlot(AllBcells, features = c("LGALS1","LGALS3","LGALS9"),pt.size = 0, group.by = "B_cell_type")

```

```{r}
rm(AllBcells)
```

## Correlation with Glofitamab response 
### All cell type 
```{r}

AllSample_subset <- subset(AllSample, Sample_code %in% Sample_list)
rm(AllSample)
VlnPlot(AllSample_subset,
            features = c("LGALS1","LGALS3","LGALS9"),
            group.by = "Response_type_total",
            pt.size = 0,
            raster = FALSE)
rm(AllSample_subset)
```
### In Monocytes
**Only One sample Low responder vs 5 High Responders**
```{r}
AllSample_subset_monocytes_response <- subset(AllSample_subset_monocytes, Sample_code %in% Sample_list)
VlnPlot(AllSample_subset_monocytes_response,
            features = c("LGALS1","LGALS3","LGALS9"),
            group.by = "Response_type_total",
            pt.size = 0,
            raster = FALSE)

rm(AllSample_subset_monocytes)
```
```{r}
# AllSample_subset_monocytes_metadata <- AllSample_subset_monocytes@meta.data |> 
#   mutate(cell_id = rownames(AllSample_subset_monocytes_metadata)) |> 
#   mutate(cell_id = gsub("[.]", "_", cell_id))
  
```

### In CD4 T-cells
```{r}

Tcells_CD4_subset <- subset(Tcells_TCD4, Sample_code %in% Sample_list)

VlnPlot(Tcells_CD4_subset,
            features = c("LGALS1","LGALS3","LGALS9"),
            group.by = "Response_type_total",
            pt.size = 0,
            raster = FALSE)
rm(Tcells_TCD4)
```

```{r}
# VlnPlot(Tcells_CD4_subset,
#         features = c("LGALS1"),
#         group.by = "Response_type_total",
#         split.by = "T_clusters",
#         pt.size = 0,
#         raster = FALSE) & 
#   scale_fill_manual(values = colors_response_type)
#         
#         VlnPlot(Tcells_CD4_subset,
#         features = c("LGALS3"),
#         group.by = "Response_type_total",
#         split.by = "T_clusters",
#         pt.size = 0,
#         raster = FALSE)
#         
#         
# VlnPlot(Tcells_CD4_subset,
#         features = c("LGALS9"),
#         group.by = "Response_type_total",
#         split.by = "T_clusters",
#         pt.size = 0,
#         raster = FALSE)
```

#### Treg Only

```{r}
Tcells_CD4_Treg_subset <- subset(Tcells_TCD4_Treg, Sample_code %in% Sample_list)
VlnPlot(Tcells_CD4_Treg_subset,
        features = c("LGALS1","LGALS3","LGALS9"),
        group.by = "Response_type_total",
        pt.size = 0,
        raster = FALSE
)
```

```{r}
  # Tcells_subset <- subset(Tcells, Cell_type %in% c("CD4") & Sample_code %in% Sample_list)
  # Tcells_subset <- subset(Tcells, T_clusters %in% c("CD4_Treg") & Sample_code %in% Sample_list)

```

```{r}
#   gene <- paste0("LGALS9")
#
#   data_Expression <- FetchData(Tcells_subset, vars = gene) %>%
#     mutate(cell_id = rownames(.)) %>%
#     mutate(cell_id = gsub("[.]", "_", cell_id)) %>%
#     left_join(Tcells_Sample_metadata)
#
#   grouped_data <- data_Expression %>%
#     group_by(B_cell_depletion_total_glofi, Sample_code, Response_type_total) %>%
#     summarise(mean_gene = mean(!!sym(gene), na.rm = TRUE), count = n())
#
#   # Calculer le modèle linéaire pour obtenir R^2
#   correlation_result <- cor.test(grouped_data$B_cell_depletion_total_glofi, grouped_data$mean_gene, use = "pairwise.complete.obs")
#   r_value <- correlation_result$estimate # Coefficient de corrélation
#   p_value <- correlation_result$p.value # Valeur p
#
#   p <- ggplot(data = grouped_data, aes(x = B_cell_depletion_total_glofi, y = mean_gene)) +
#     geom_smooth(method = "lm", color = "black", fill = "gray80", linewidth = 0.8) +
#     geom_point(aes(fill = Response_type_total),
#       shape = 21,
#       color = "black",
#       position = position_dodge(0),
#       size = 3, stroke = 0.5, alpha = 0.9
#     ) +
#     scale_fill_manual(values = colors_response_type) +
#     labs(
#       title = "",
#       x = "B-Cell depletion at D6",
#       y = expression(bolditalic("LGALS9") * bold(" in CD3 T-Cells"))
#     ) +
#     # theme_blood_fig3() +
#     theme(legend.position = "none") # Ajuster la taille du texte de l'axe y
#
#   # Ajouter l'annotation
#  p + annotation_custom(
#     grob = textGrob(
#       label = sprintf("R = %.4f\n𝑝 = %.2e", r_value, p_value),
#       x = unit(0.05, "npc"), y = unit(0.25, "npc"),
#       hjust = 0, vjust = 1,
#       gp = gpar(fontsize = 8, col = "black", face = "bold")
#     )
#   )
```

