---
title: "Sc_RNAseq_GAL9"
author: "Paul Marcoux"
date: today
date-format: "YYYY-MM-DD"
format: 
  html:
    page-layout: full
    toc: true
    toc-depth: 3
    toc-location: left
    code-fold: true
    echo: false
    code-summary: "Show code"
    code-tools: true
    theme: cosmo
    embed-resources: false
    number-sections: true
execute:
  warning: false
  message: false
  freeze: auto
  fig-width: 12
  column: page
---

# Analyse of B-NHL scRNAseq data

## Open Data & Review

```{r}
# #| include: false
library(here)
library(gtools)
source(here('src/00_Open_metadata.R'))
source(here('src/01_Open_sc_files.R'))
```

```{r}
Data_info_patients <- Metadata_All |> select(Sample_code,Origin,RD,Disease) |> distinct() 

Data_info_patients <- Data_info_patients[mixedorder(Data_info_patients$Sample_code), ]
knitr::kable(Data_info_patients)

```

## All data

### Umap

```{r}
DimPlot(AllSample,
        reduction = "umap_all",
        label = FALSE,
        pt.size = 0.01,
        raster = FALSE,
        group.by = "Sample_code",
        alpha = 0.3
) 
DimPlot(AllSample,
        reduction = "umap_all",
        label = FALSE,
        pt.size = 0.01,
        raster = FALSE,
        group.by = "Cell_type",
        alpha = 0.3
) 
```

### GAL9 by disease
**Expression of GAL9 increase in tFl/DLBCL compared to FL.**

```{r}
VlnPlot(AllSample,
            features = c("LGALS9"),
            group.by = "Disease",
            pt.size = 0,
            raster = FALSE
)
```



**What Cell type are expressing GAL9? **
```{r}
FeaturePlot(AllSample,
            features = c("LGALS9"),
            reduction = "umap_all",
            split.by = "Disease",
            pt.size = 0.01,
            raster = FALSE
)
```

**GAL9 is expressed mostly by Monocytes, and to a lesser extent by CD4 T-Cells and NK Cells.**
```{r}
VlnPlot(AllSample,
        features = c("LGALS9"),
        group.by = "Disease",
        split.by = "Cell_type",
        pt.size = 0,
        raster = FALSE
)
```

## Monocytes Only

```{r}
#| cache: false
AllSample_subset_monocytes <- subset(AllSample, Cell_type %in% "Monocytes")
```
### Gal9 in Monocytes
```{r}
#| warning: false
VlnPlot(AllSample_subset_monocytes,
        features = c("LGALS9"),
        group.by = "Disease",
        split.by = "Cell_type",
        pt.size = 0,
        raster = FALSE
)

FeaturePlot(AllSample_subset_monocytes,
            features = c("LGALS9"),
            reduction = "umap_all",
            split.by = "Disease",
            pt.size = 0.01,
            raster = FALSE) +
  plot_layout(guides = "collect") &
  xlim(c(0,10)) &
  ylim(c(7,NA))

```


### Identification of Monocytes 
#### Umap of Monocytes only by cluster and disease
**Monocytes only from PBMC samples.**
```{r}
DimPlot(AllSample_subset_monocytes,
            reduction = "umap_all",
            group.by = "Origin",
            pt.size = 0.01,
            raster = FALSE) +
  plot_layout(guides = "collect") &
  xlim(c(0,10)) &
  ylim(c(7,NA))
```
**Very few Monocytes from DLBCL samples**
```{r}

DimPlot(AllSample_subset_monocytes,
            reduction = "umap_all",
            group.by = "Disease",
            pt.size = 0.01,
            raster = FALSE) +
  plot_layout(guides = "collect") &
  xlim(c(0,10)) &
  ylim(c(7,NA))
```

```{r}
DimPlot(AllSample_subset_monocytes,
            reduction = "umap_all",
            group.by = "integrated_snn_res.0.3",
            pt.size = 0.01,
            raster = FALSE) +
  plot_layout(guides = "collect") &
  xlim(c(0,10)) &
  ylim(c(7,NA))

```
 

#### Feature Plots of Monocytes Markers
```{r Identification Macrophages}
markers_scRNA <- c(
  # Pan-monocytes/macrophages
  "CD14", "FCGR3A", "CSF1R", "CD68",
  
  # Mono classiques vs non-classiques
  "S100A8", "VCAN", "CX3CR1", "CDKN1C",
  
  # Sous-types macrophages
  "FCN1",    # inflammatoires
  "FOLR2",   # résidents
  "SPP1",    # fibrotiques
  "TREM2",   # immunosuppresseurs

  
  # Activation / polarisation
  "IL1B", "TNF", "MRC1", "CD163",
  
  # Prolifération
  "MKI67"
)

FeaturePlot(AllSample_subset_monocytes,
            features = c("CD14", "FCGR3A", "CSF1R", "CD68"),
            reduction = "umap_all",
            pt.size = 0.01,
            raster = FALSE) +
  plot_layout(guides = "collect") &
  xlim(c(0,10)) &
  ylim(c(7,NA))

FeaturePlot(AllSample_subset_monocytes,
            features = c("S100A8", "VCAN", "CX3CR1", "CDKN1C"),
            reduction = "umap_all",
            pt.size = 0.01,
            raster = FALSE) +
  plot_layout(guides = "collect") &
  xlim(c(0,10)) &
  ylim(c(7,NA))

FeaturePlot(AllSample_subset_monocytes,
            features = c("FCN1", "FOLR2", "SPP1", "TREM2","MKI67"),
            reduction = "umap_all",
            pt.size = 0.01,
            raster = FALSE) +
  plot_layout(guides = "collect") &
  xlim(c(0,10)) &
  ylim(c(7,NA))

FeaturePlot(AllSample_subset_monocytes,
            features = c("IL1B", "TNF", "MRC1", "CD163"),
            reduction = "umap_all",
            pt.size = 0.01,
            raster = FALSE) +
  plot_layout(guides = "collect") &
  xlim(c(0,10)) &
  ylim(c(7,NA))

```



